---
title: "Reusing code-chunks"
author: "Tonya Severson"
date: "12/02/2021"
output: 
  github_document:
    fig_width: 7
    fig_height: 5
    keep_html: FALSE
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

After working on a project for a while, R markdown files and versions seem to proliferate. R markdown provides several ways to read code from external Rscripts, making it possible to reuse code and reduce repetition.

## Place code in external Rscript

* Code-chunks (figures, dataframes)  
  - `## ---- chunk-name`
  - Can have one or more chunks
  - Can use single # for comments
* Source (variables and functions)
  -e.g., file paths

## Read chunks from external code

```{r read-code, echo=TRUE, cache=FALSE}
# Two of the ways to read in code
knitr::read_chunk('src/iris_data_analysis.R')
source('src/external_functions.R') 
```

* Insert a code chunk to read code from external file
* Chunk option `cache=FALSE` is recommended

## Use chunks in Rmd file

```{r iris-pivoted, echo=FALSE}
# I find it useful to record name of file where code-chunk is located: iris_data_analysis.R
# `iris-pivoted` code chunk produces the head of the iris df
# To hide code in knitted outputs, use 
```

## Can also read in code to render plots

```{r, iris-boxplot, echo=FALSE, fig.height=5}

# Second chunk from iris_data_analysis.R

```

## Or use function or variables from external files

```{r functions, include=FALSE, echo=FALSE}

# sourced in read-chunks chunk from 'src/external_functions.R'

answer <- multiply_values(6, 7)

hello <- myHW

vec <- print(ridiculous_repetition(myHW, 10), quote = FALSE)

```

* The answer is `r answer`
* `r hello`
* Enthusiastic greeting: `r vec`

## Useful links about reusing code


* https://bookdown.org/yihui/rmarkdown-cookbook/managing-projects.html
  - Source external scripts (16.1)
  - Multiple code chunks (16.3)

